Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-17 doc/manuscript/ESSDmanuscript.Rmd

Forest ecosystem C stocks may be parsed into pools in various ways. 
IPCC parses into biomass (aboveground and belowground), dead organic matter (dead wood and litter), and soil organic matter (Table 1).
Quantifying these requires a one-time measurement.

\newpage

**Table 1: variables with definitions and measurement methods.** Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance). (*Currently adding this as a figure (generated from original draft) because kableExtra doesn't seem to work in this template, and I can't quickly get the template format to work. Table that we want here is "figures_tables/C_pools.csv"*)

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Table 1"}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/C_pools_fig.png")
```

```{r eval = FALSE, echo=FALSE, warning=FALSE}
#another failed attempt at the table
library(flextable)
C_pools_table <- read.csv("figures_tables/C_pools.csv")
ft <- flextable(C_pools_table)
ft

```

\begin{table*}[t]
\caption{This is a start at table 1 using the template format. }
\begin{tabular}{l c c c r}
\tophline

pool & subpool & definition & major sources of estimate variation & IPCC guidance \\
\middlehline
biomass & aboveground & all biomass of living vegetation, both woody and herbaceous, above the soil & allometry, min dbh & acceptable to exclude understory  \\

\bottomhline
\end{tabular}
\belowtable{I don't know how to adjust so that it doesn't run off the page.}
\end{table*}

>>>>

Forest ecosystem C stocks may be parsed into pools in various ways. 
IPCC parses into biomass (aboveground and belowground), dead organic matter (dead wood and litter), and soil organic matter (Table&nbsp;\@ref(table_variables)).
Quantifying these requires a one-time measurement.

```{r table_variables, eval = TRUE, echo=FALSE, warning=FALSE}
C_pools_table <- read.csv("figures_tables/C_pools.csv")
names(C_pools_table) <- stringr::str_replace_all(names(C_pools_table), "\\.", " ")

library(knitr)
library(kableExtra)
knitr::kable(C_pools_table, format = "latex",
             longtable = FALSE,
             caption = "\\textbf{Variables with definitions and measurement methods.} Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance).") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)
```
